Minitutorial 1
========================================================

With the aim to provide an example of a complete workflow and to show some useful *techniques* and *functions* when **programming in R** (including how to get the most out of the **documentation**), I have created this *R script*.

Using the local help
--------------------
### Searching for functions:
First and foremost we should be able to handle the **base** library.  

I encourage you to review its documentation by running the next command,
```{r}
library(help=base)
```
and checking each of the functions contained in it by using the **help()** function or the question operator **?**, for example:
```{r}
help("Control")
```

Since usually the name of a function is closely related to the action it performs, it's useful to try to find functions either by a keyword which can be a whole word, an abbreviation, or an acronym, for example:

```{rdir}
apropos("help")
```
Let's type:
```{r localhelp,tidy=FALSE,echo=TRUE}
?help.search;
```
We see the function **help.search()** can take several *parameters*.  

We will use by now only the arguments *pattern* and *package*.
```{r localhelpex}
help.search("remove objects", package = "base");
```
The help page returns:  
 ----
>    **base::rm**      Remove Objects from a Specified Environment  

 ----
If we go to the end of the help page we'll see the following example:  
 ----
>  **rm**(**list** = **ls**())  

 ----  

So, list is one of the arguments of the **rm()** AKA **remove()** function.  

In order to see what the function **ls()** does, type:
```{rls,tidy=FALSE}
?ls();
```

### Find the package a function belongs to:
We can double-check **rm()** really belongs to the base package by using the function **find()**
```{rfind}
find("rm")
```
### Run examples:
You can also run the existing examples for a particular function by using the **example()** function.
```{r examples}
example(rm);
```
Vignettes
---------
A "vignette" is a special type of **documentation** that several but not all packages have included.  

When it exists, is the most important source of help for dealing with a particular package.  

You can browse all the vignettes you have at your local R installation the following way:  
### Browse local vignnetes:
```{r browsevignettes}
browseVignettes(all=T);
```
The **browseVignettes()** function opens your default web browser and displays a list of the available vignettes at your computer and hyperlinks to open them.  

### Review local vignette:
For viewing the vignette for a particular library you can use the **vignette()** function, or via the the **browseVignettes()**:
```{r vignette}
vignette("Sweave");
```
This will open (usually) a **.pdf** or an **.html** file with the required vignette.

### Review local vignette:
```{r vigbrowser}
browseVignettes("knitr");
```
The Rdocumentation page
-----------------------
A very nice tool for searching and reading the documentation has been built by the rdocumentation.org.  

From the web page:
 ---
> Rdocumentation is a tool that helps you easily find and browse the documentation of all current and some past packages on CRAN.

 ---
```{r rdocumentation}
# Uncomment if you want to go to the web page
browseURL("http://www.rdocumentation.org/")
```
### The Rdocumentation package:
There is also a package for using the "rdocumentation" tool inside R.  

It can be found on GitHub.
```{r rdocumentationgit}
# Uncomment if you want to go to the web page
browseURL("https://github.com/Data-Camp/Rdocumentation")
```

So let's install it:

### Installing from GitHub:
```{rdevtools}
library(devtools)
install_github("Rdocumentation","Data-Camp")
```
### Using the Rdocumentation package
```{rRdocEx, tidy=FALSE}
library(Rdocumentation)
?rm
```
Note Rdocumentation masks the help, so you are redirected to the Rdocumentation web page for reading the help.  

I found it very handy, mostly due the way the help is displayed, because let's face it, the local R documentation is plain, ugly, and difficult to read.

Now that you know this option exists, let's keep using the local help for the rest of this mini-tutorial.

### Unloading a library from a session:
```{r}
detach("package:Rdocumentation", unload=TRUE)
```
