Minitutorial 3
========================================================

Checking headings
-----------------
Now, I would like to know if all headings or column names for all files
are the same, before doing anything else with those data.

So, the first thing I'll do is to get all file names into a vector
```{r}
mylocal.path <- "C:/Users/Diego/Documents/GitHub/R-Notes";
setwd(mylocal.path);
specdata.files <- dir("./specdata", full.names=T);
```
Let's check what kind of object R just built:
```{r}
is(specdata.files);
```
Since I don't know how many columns each file has, I'll need to use a list
of lists. This is because a data frame or a matrix will truncate the
number of columns after the first element gets inserted.  

Let's initialize our list first:
```{r}
file.headings <- list();
```
Now let's loop through all files and get their headings:
```{r}
for(i in 1:length(specdata.files)){
 
 file.headings <- append(file.headings, 
                         list(names(read.csv(specdata.files[i],nrows = 1))))
};
```
Let's check the unique headings:
```{r}
unlist(unique(file.headings));
```
Now let's see if all files have the same headings.
For that I'm going to compare all captured headings against the resultant
unique headings.
Let's first store the list of unique headings into a variable.
```{r}
unique.headings <- unique(file.headings);
```
Before starting the comparisons, I'm going to create a logical vector, or
in other words, a vector that will contain only TRUE or FALSE values for
storing the results of the comparisons.
```{r}
 equal.headings <- vector();
```
Now let's run the comparisons:
```{r}
   for(i in 1:length(file.headings)){
     equal.headings <- c(equal.headings, 
                         identical(unique.headings, file.headings[i]))
   };
```
Let's check how many comparisons returned FALSE:
```{r}
length(equal.headings[equal.headings==F]);
```
And how many returned TRUE:
```{r}
 length(equal.headings[equal.headings==T]);
```
In case we wanted to know which files returned TRUE or FALSE, we could use
the which() function:
```{r}
which(equal.headings==F);
which(equal.headings==T);
```
As you can see, the which function returns the indexes, not the actual
name of the files. But we can use that for subsetting our vector
'specdata.files':
```{r}
specdata.files[which(equal.headings==T)];
```

